\ttitle

### 2013-06-28 Appendices/AppendixB-camci.tex
Added refs, comparing stuff

*** Thus methods of data descriptions should be compared (which are more general) and not only density estimation? ***

@@

@@

@@

\subsection{Novelty/outlier detection}
\subsection{Scale parameter}
\subsection{Robust statistics / "M-Estimators"}
Is the method robust, in the sense that outliers have restricted impact on the quality.

>>>>

*** \emph{Thus methods of data descriptions should be compared (which are more general) and not only density estimation?} ***

The paper of Yin \etal \cite{yin2008sensor} makes a distinction between similarity based (using a defined distance measure) and model based (which characterize the data using predictive models) approach.
The one-class SVM is used in the model-approach to filter out normal activities in order to detect abnormality behavior.

@@

*** TODO: make a clear distinction between model types; similarity (distance based) or model based, as in \cite{yin2008sensor} ***

@@

%-------------------------

Re-evaluatie \cite{guo2012adaptive}, uses (amongst others) a pca-based dimension-detection method (?).
Also uses model-selection as an intermediate step.

@@

\subsection{Novelty/outlier detection}
*** Read \cite{hodge2004survey} ``A survey of outlier detection methodologies'' to compare with other methodologies. ***

\subsection{Scale parameter}
\subsection{Robust statistics / "M-Estimators"}
Is the method robust, in the sense that outliers have restricted impact on the quality.
